The SMT Competition 2015--2018

### 2018-10-08 2018/report/SMT-COMP.tex
Work in progress

\begin{abstract}
  The International Satisfiability Modulo Theories Competition is an
  annual competition between Satisfiability Modulo Theories solvers.
  We report on the design and selected results of the competition
  during the last FLoC Olympiad, from 2015 to 2018. \TODO: some
  notable observations/conclusions?
\end{abstract}

@@

Satisfiability Modulo Theories (SMT) is a generalization of Boolean
satisfiability (SAT), the satisfiability decision problem for
propositional logic.  In place of Boolean variables, SMT formulas may
contain terms that are built from function and predicate symbols drawn
from a number of background theories.  Background theories, which are
typically motivated by application areas, include the theory of
arrays, integer and real arithmetic, bit-vectors, and floating-point
numbers among others.  For instance, the following is an SMT formula
over the combination of integer arithmetic and uninterpreted
functions:
$$TODO$$
Software tools to determine the satisfiability of such formulas are
called SMT solvers.

@@

The International Satisfiability Modulo Theories Competition
(SMT-COMP) is an annual competition between SMT solvers.  It is
affiliated with the International Workshop on Satisfiability Modulo
Theories.  Solvers are submitted to the competition by their
developers, and pitted against each other in a number of tracks and
divisions.  The SMT Competition was part of the Federated Logic
Conference (FLoC) Olympic Games in~2014, and again in~2018.  It was
last described in a 2014 competition report~\cite{TODO}.  In this
paper, we report on the design and selected results of the competition
during the last FLoC Olympiad, from 2015 to 2018.

@@

Each year, the SMT Workshop includes a block of time to present the
competitors and results of the competition.  The workshop is
affiliated with a different conference each year: with CAV in 2015,
with IJCAR in 2016, again with CAV in 2017, and with FLoC in 2018.
Consequently, its date varies by several weeks.  Competition results
were presented on July~19 in 2015, on July~2 in 2016, on July~23 in
2017, and on July~13 in 2018.

Important deadlines are effectively determined by calculating
backwards from the date of the next SMT Workshop.  The competition's
computational workload should be completed approximately two weeks
before the workshop date, to give participants and other parties a
chance to scrutinize the data for errors, allow partial re-runs of
competition jobs if necessary, and give the organizers time to prepare
the results presentation.  While making all data publicly available
well in advance of the official results presentation may impact the
suspense, it has on several occasions helped to uncover serious
problems with the competition tools or the StarExec framework (see
Section~\ref{sec:starexec}) that could have led to invalid results if
they had gone unnoticed.
\begin{tjark}
  Discuss these issues somewhere, add (forward?) reference here.
\end{tjark}

@@

\section{Other Competitions}
\label{sec:OtherCompetitions}

@@

\section{FLoC Olympic Games Scoring}
\label{sec:floc}

@@

\section{Concluding Observations and Recommendations}
\label{sec:conclusions}

@@

\bibliographystyle{plainbv}
%\bibliography{SMT-COMP}

>>>>

\begin{abstract}
  The International Satisfiability Modulo Theories Competition is an
  annual competition between Satisfiability Modulo Theories~(SMT)
  solvers.  The 2018 edition of the competition was part of the FLoC
  Olympic Games, which comprised 14 competitions in various areas of
  computational logic.  We report on the design and selected results
  of the SMT Competition during the last FLoC Olympiad, from 2015 to
  2018. \TODO: some notable observations/conclusions?
\end{abstract}

@@

Satisfiability Modulo Theories (SMT) is a generalization of Boolean
satisfiability (SAT), the satisfiability decision problem for
propositional logic.  In place of Boolean variables, SMT formulas may
contain terms that are built from function and predicate symbols drawn
from a number of background theories.  Background theories, which are
typically motivated by application domains, include the theory of
arrays~\cite{TODO}, integer and real arithmetic~\cite{TODO},
bit-vectors~\cite{TODO}, and floating-point numbers~\cite{TODO} among
others.  For instance, the following is an SMT formula over the
combination of integer arithmetic and uninterpreted functions:
%
$$x \leq y \wedge y \leq x \wedge P (f(x) - f(y)) \wedge \neg P(0)$$
%
Software tools to determine the satisfiability of such formulas are
called SMT solvers.  With its rich input language, SMT has
applications in software engineering, optimization, and many other
areas~\cite{DeMoura:2011:SMT}.

@@

The International Satisfiability Modulo Theories Competition
(SMT-COMP) is an annual competition between SMT solvers.  It is
affiliated with the International Workshop on Satisfiability Modulo
Theories.  Solvers are submitted to the competition by their
developers, and pitted against each other in a number of tracks and
divisions.  The SMT Competition was part of the Federated Logic
Conference (FLoC) Olympic Games, which comprised 14 competitions in
various areas of computational logic, in Vienna in~2014, and again in
Oxford~(UK) in~2018.  It was last described in a 2014 competition
report~\cite{DBLP:journals/jsat/CokDW14}.  In this paper, we report on
the design and selected results of the competition during the last
FLoC Olympiad, from 2015 to~2018.

@@

Each year, the SMT Workshop includes a block of time to present the
competitors and results of the competition.  The workshop is
affiliated with a different conference each year: with CAV in 2015,
with IJCAR in 2016, again with CAV in 2017, and with FLoC in~2018.
Consequently, its date varies by several weeks.  Competition results
were presented on July~19 in 2015, on July~2 in 2016, on July~23 in
2017, and on July~13 in 2018.

Important deadlines are effectively determined by calculating
backwards from the date of the next SMT Workshop.  The competition's
computational workload should be completed approximately two weeks
before the workshop date, to give participants and other parties a
chance to scrutinize the data for errors, allow partial re-runs of
competition jobs if necessary, and give the organizers time to prepare
the results presentation.  While making all data publicly available
well in advance of the official results presentation may impact the
suspense, it has on several occasions helped to uncover serious
problems with the competition tools or the StarExec framework (see
Section~\ref{sec:starexec}) that could have led to invalid results
otherwise.
\begin{tjark}
  Discuss these issues somewhere, add (forward?) reference here.
\end{tjark}

@@

@@

\section{FLoC Olympic Games}
\label{sec:floc}

In 2014, the SMT Competition was part of the FLoC Olympic Games, which
sponsored three Kurt G\"odel medals.  After substantial internal
debate, the competition organizers decided to award these to the
winner of the QF\_BV logic (which has historically been the logic with
the largest number of solver submissions), as well as to the two best
main-track solvers according to a competition-wide ranking that had
been instituted especially for this
purpose~\cite{DBLP:journals/jsat/CokDW14}.

The 2018 edition of the competition was again part of the FLoC Olympic
Games.  After last-minute negotiations with the Olympic Games
organizers, it was decided that the SMT Competition would award seven
Kurt G\"odel medals.  The competition organizers gave these to the
following solvers:
\begin{itemize}
\item The best three main-track solvers according to the
  competition-wide scoring (first place: CVC4, second place:
  Yices-2.6.0, third place: SMTInterpol);
\item the solver that won the most competitive divisions in the
  application track (Yices-2.6.0);
\item the solver that won the most competitive divisions in the
  unsat-core track (Yices-2.6.0);
\item the solver(s) that won the QF\_BV division in the main track
  (sequential ranking: Boolector, parallel ranking: Minkeyrink-MT)
\end{itemize}

The competition-wide ranking that was used in~2018 was a refinement of
the ranking scheme introduced in~2014.  A contentious issue has been
the treatment of incorrect solver results in this ranking.  While
incorrect answers cause a solver to be ranked behind all correct
solvers in the per-division ranking (see \TODO )

@@

\section{Conclusions}
\label{sec:conclusions}

@@

\bibliographystyle{plainbv} \bibliography{SMT-COMP}
